Figure 5 - IP-MS

### 2024-07-15 ms_figure_5_ipms.Rmd
Use strict/lenient cutoff (Fig 5)

The 'high stringency' thresholds correspond to an adjusted p-value cutoff of 
`r adjpThreshold` and a log2 fold change cutoff of `r log2fcThreshold`.
The 'low stringency' thresholds correspond to an adjusted p-value cutoff of 
`r adjpThresholdLoose` and a log2 fold change cutoff of `r log2fcThreshold`.

@@

makeInteractorSummary(sce = sce150, baitdata = baitdata_150, adjp_cutoff = adjpThreshold,
                      logfc_cutoff = log2fcThreshold, idmap = idmap, 
                      baits_to_keep = baitclass$Gene_name[baitclass$class != "nobait"],
                      tbl_title = "150 mM, high stringency") |>
    dplyr::full_join(
        makeInteractorSummary(sce = sce500, baitdata = baitdata_500, adjp_cutoff = adjpThreshold,
                              logfc_cutoff = log2fcThreshold, idmap = idmap, 
                              baits_to_keep = baitclass$Gene_name[baitclass$class != "nobait"],
                              tbl_title = "500 mM, high stringency")
    ) |> 
    dplyr::full_join(
        makeInteractorSummary(sce = sce150, baitdata = baitdata_150_loose, adjp_cutoff = adjpThresholdLoose,
                              logfc_cutoff = log2fcThreshold, idmap = idmap, 
                              baits_to_keep = baitclass$Gene_name[baitclass$class != "nobait"],
                              tbl_title = "150 mM, low stringency")
    ) |>
    dplyr::full_join(
        makeInteractorSummary(sce = sce500, baitdata = baitdata_500_loose, adjp_cutoff = adjpThresholdLoose,
                              logfc_cutoff = log2fcThreshold, idmap = idmap, 
                              baits_to_keep = baitclass$Gene_name[baitclass$class != "nobait"],
                              tbl_title = "500 mM, low stringency")
    ) |>
    kbl() |>
    kable_styling()
```

@@

## Pie chart, within-vs-between DBD family interactions
pie_data_150 <- baitdata_150$nbrIntMat |>
    filter(bait != "Untagged") |>
    select(nbrTFs_samefam, nbrTFs_difffam) |>
    pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
    group_by(class) |>
    summarize(nbrTF = sum(nbrTF), .groups = "drop")
pie_bait_150 <- ggplot(
    pie_data_150,
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    geom_segment(x = 1.55, xend = 1.55, 
                 y = 0, yend = exp_same * sum(pie_data_150$nbrTF),
                 linewidth = 1.5) + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "150 mM NaCl\nstrict cutoff") + 
    theme_void()
```

@@

## Pie chart, within-vs-between DBD family interactions
pie_data_150_loose <- baitdata_150_loose$nbrIntMat |>
    filter(bait != "Untagged") |>
    select(nbrTFs_samefam, nbrTFs_difffam) |>
    pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
    group_by(class) |>
    summarize(nbrTF = sum(nbrTF), .groups = "drop")
pie_bait_150_loose <- ggplot(
    pie_data_150_loose,
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    geom_segment(x = 1.55, xend = 1.55, 
                 y = 0, yend = exp_same * sum(pie_data_150_loose$nbrTF),
                 linewidth = 1.5) + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "150 mM NaCl\nlenient cutoff") + 
    theme_void()
```

@@

## Pie chart, within-vs-between DBD family interactions
pie_data_500 <- baitdata_500$nbrIntMat |>
    filter(bait != "Untagged") |>
    select(nbrTFs_samefam, nbrTFs_difffam) |>
    pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
    group_by(class) |>
    summarize(nbrTF = sum(nbrTF), .groups = "drop")
pie_bait_500 <- ggplot(
    pie_data_500,
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    geom_segment(x = 1.55, xend = 1.55, 
                 y = 0, yend = exp_same * sum(pie_data_500$nbrTF),
                 linewidth = 1.5) + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "500 mM NaCl\nstrict cutoff") + 
    theme_void()
```

@@

## Pie chart, within-vs-between DBD family interactions
pie_data_500_loose <- baitdata_500_loose$nbrIntMat |>
    filter(bait != "Untagged") |>
    select(nbrTFs_samefam, nbrTFs_difffam) |>
    pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
    group_by(class) |>
    summarize(nbrTF = sum(nbrTF), .groups = "drop")
pie_bait_500_loose <- ggplot(
    pie_data_500_loose,
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    geom_segment(x = 1.55, xend = 1.55, 
                 y = 0, yend = exp_same * sum(pie_data_500_loose$nbrTF),
                 linewidth = 1.5) + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "500 mM NaCl\nlenient cutoff") + 
    theme_void()
```

>>>>

The 'strict cutoff' thresholds correspond to an adjusted p-value cutoff of 
`r adjpThreshold` and a log2 fold change cutoff of `r log2fcThreshold`.
The 'lenient cutoff' thresholds correspond to an adjusted p-value cutoff of 
`r adjpThresholdLoose` and a log2 fold change cutoff of `r log2fcThreshold`.

@@

makeInteractorSummary(sce = sce150, baitdata = baitdata_150, adjp_cutoff = adjpThreshold,
                      logfc_cutoff = log2fcThreshold, idmap = idmap, 
                      baits_to_keep = baitclass$Gene_name[baitclass$class != "nobait"],
                      tbl_title = "150 mM, strict cutoff") |>
    dplyr::full_join(
        makeInteractorSummary(sce = sce500, baitdata = baitdata_500, adjp_cutoff = adjpThreshold,
                              logfc_cutoff = log2fcThreshold, idmap = idmap, 
                              baits_to_keep = baitclass$Gene_name[baitclass$class != "nobait"],
                              tbl_title = "500 mM, strict cutoff")
    ) |> 
    dplyr::full_join(
        makeInteractorSummary(sce = sce150, baitdata = baitdata_150_loose, adjp_cutoff = adjpThresholdLoose,
                              logfc_cutoff = log2fcThreshold, idmap = idmap, 
                              baits_to_keep = baitclass$Gene_name[baitclass$class != "nobait"],
                              tbl_title = "150 mM, lenient cutoff")
    ) |>
    dplyr::full_join(
        makeInteractorSummary(sce = sce500, baitdata = baitdata_500_loose, adjp_cutoff = adjpThresholdLoose,
                              logfc_cutoff = log2fcThreshold, idmap = idmap, 
                              baits_to_keep = baitclass$Gene_name[baitclass$class != "nobait"],
                              tbl_title = "500 mM, lenient cutoff")
    ) |>
    kbl() |>
    kable_styling()
```

@@

## Pie chart, within-vs-between DBD family interactions
pie_data_150 <- baitdata_150$nbrIntMat |>
    filter(bait != "Untagged") |>
    select(nbrTFs_samefam, nbrTFs_difffam) |>
    pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
    group_by(class) |>
    summarize(nbrTF = sum(nbrTF), .groups = "drop") |>
    mutate(ypos = sum(nbrTF) - cumsum(nbrTF) + 0.5 * nbrTF)
pie_bait_150 <- ggplot(
    pie_data_150,
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    geom_segment(x = 1.55, xend = 1.55, 
                 y = 0, yend = exp_same * sum(pie_data_150$nbrTF),
                 linewidth = 1.5) + 
    geom_text(aes(y = ypos, label = nbrTF), size = 7, color = "black") + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "150 mM NaCl\nstrict cutoff") + 
    theme_void()
```

@@

## Pie chart, within-vs-between DBD family interactions
pie_data_150_loose <- baitdata_150_loose$nbrIntMat |>
    filter(bait != "Untagged") |>
    select(nbrTFs_samefam, nbrTFs_difffam) |>
    pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
    group_by(class) |>
    summarize(nbrTF = sum(nbrTF), .groups = "drop") |>
    mutate(ypos = sum(nbrTF) - cumsum(nbrTF) + 0.5 * nbrTF)
pie_bait_150_loose <- ggplot(
    pie_data_150_loose,
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    geom_segment(x = 1.55, xend = 1.55, 
                 y = 0, yend = exp_same * sum(pie_data_150_loose$nbrTF),
                 linewidth = 1.5) + 
    geom_text(aes(y = ypos, label = nbrTF), size = 7, color = "black") + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "150 mM NaCl\nlenient cutoff") + 
    theme_void()
```

@@

## Pie chart, within-vs-between DBD family interactions
pie_data_500 <- baitdata_500$nbrIntMat |>
    filter(bait != "Untagged") |>
    select(nbrTFs_samefam, nbrTFs_difffam) |>
    pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
    group_by(class) |>
    summarize(nbrTF = sum(nbrTF), .groups = "drop") |>
    mutate(ypos = sum(nbrTF) - cumsum(nbrTF) + 0.5 * nbrTF)
pie_bait_500 <- ggplot(
    pie_data_500,
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    geom_segment(x = 1.55, xend = 1.55, 
                 y = 0, yend = exp_same * sum(pie_data_500$nbrTF),
                 linewidth = 1.5) + 
    geom_text(aes(y = ypos, label = nbrTF), size = 7, color = "black") + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "500 mM NaCl\nstrict cutoff") + 
    theme_void()
```

@@

## Pie chart, within-vs-between DBD family interactions
pie_data_500_loose <- baitdata_500_loose$nbrIntMat |>
    filter(bait != "Untagged") |>
    select(nbrTFs_samefam, nbrTFs_difffam) |>
    pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
    group_by(class) |>
    summarize(nbrTF = sum(nbrTF), .groups = "drop") |>
    mutate(ypos = sum(nbrTF) - cumsum(nbrTF) + 0.5 * nbrTF)
pie_bait_500_loose <- ggplot(
    pie_data_500_loose,
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    geom_segment(x = 1.55, xend = 1.55, 
                 y = 0, yend = exp_same * sum(pie_data_500_loose$nbrTF),
                 linewidth = 1.5) + 
    geom_text(aes(y = ypos, label = nbrTF), size = 7, color = "black") + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "500 mM NaCl\nlenient cutoff") + 
    theme_void()
```
